Market simulator

### 2020-10-13 analysis/05_market_simulator.Rmd
Trying to get update button to work

# Initial organization configuration
organization_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'org_data_test1.csv')
)

>>>>

# Initial organization configuration
organization_data <- reactive({ 
  read_csv(
    here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  )
})
